\vskip-0.6in \Large Political Uncertainty

### 2015-03-25 GS-extension.tex
add comparative statics for B and note on why sequential model is not interesting

@@

@@

				\end{itemize}
		\end{itemize}	
	\item Vote buyer A
		\begin{itemize}
			\item Whatever we decide for vote buyer B will be the same for vote buyer A
		\end{itemize}
\end{enumerate}

>>>>

									\label{ex:objB}

@@

										\label{eq:focB}

@@

				\end{itemize}
		\end{itemize}	
	\item Vote buyer A
		\begin{itemize}
			\item Whatever we decide for vote buyer B will be the same for vote buyer A
			\item Adapting Expression~\ref{ex:objB} for Vote Buyer A
				\begin{multline}
					\max_{a(j)} \ \int_{-\frac{1}{2}}^\frac{1}{2} \left[ W_A \cdot \Phi \left(\frac{\frac{\alpha + a(j) - b(j)}{\beta} - j}{\sigma_j} \right) - b(j) \right] dj \\
						\text{subject to} \hskip.2in \int_{-\frac{1}{2}}^\frac{1}{2} a(j) dj \leq W_A  \hskip.2in \text{and} \hskip.2in a(j)\geq0 \ \forall j
							\label{ex:objA}
				\end{multline}
					\begin{itemize}
						\item Major problem if we solve this game sequentially: when substituting the FOC for Vote Buyer B (Equation~\ref{eq:focB}) into Vote Buyer A's objective function, the $a(j)$'s cancel out ($b(j)$ is linear in $a(j)$) so the benefit term is constant in $a(j)$
					\end{itemize}
		\end{itemize}
\end{enumerate}

\newpage
Comparative statics
\begin{itemize}
	\item Vote buyer B (3/25/15)
		\begin{itemize}
			\item Those for $j$, $a(j)$ and $\alpha$ don't involve the root term, so don't differ depending on whether we take the plus or minus version
				\[
					\frac{\partial b(j)}{\partial j} = -\beta \hskip.2in \frac{\partial b(j)}{\partial a(j)} = 1 \hskip.2in \frac{\partial b(j)}{\partial \alpha} = 1
				\]
			\item Those for $\beta$ and $\sigma_j$ \textit{do} involve the root term. I will only display the version for the positive root; there is also a version with all the signs reversed
				\[
				  \frac{\partial b(j)}{\partial \beta} = -j + \sigma_j \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\sigma_j}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
				\[
				  \frac{\partial b(j)}{\partial \sigma_j} = \beta \sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)} - \frac{\beta}{\sqrt{2 \left(\ln W_B - \ln \beta\sigma_j - \ln \sqrt{2\pi} \right)}}
				\]
		\end{itemize}
\end{itemize}
